---
title: "Securitizing the Republic: Figure Summary"
author: "Luan Blakaj 齐凯"
date: "`r Sys.Date()`"
output: 
  pdf_document:
    toc: true
    number_sections: true
    latex_engine: xelatex
header-includes:
  - \usepackage{float}
  - \usepackage{graphicx}
  - \usepackage{geometry}
  - \geometry{margin=1in}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.pos = "H", out.width = "90%")
```

# Introduction

This document provides a comprehensive summary of all figures generated for the thesis "Securitizing the Republic". It aggregates outputs from multiple analysis scripts, providing the methodology and interpretation for each visualization.

The figures are organized by their analytical focus:
1.  **Core Trends (A-D Series)**: Foundational continuity and displacement analysis.
2.  **Expanded Methodologies (New-A Series)**: Advanced statistical tests (volatility, structural breaks).
3.  **Additional Explorations (E-I Series)**: Recent data updates and robustness checks (E-Series was renamed to start at E to avoid conflicts).
4.  **Spatial Trajectories**: Animated and static center-of-gravity analyses.

\newpage

# Section 1: Core Trends (Source 07)

These figures establish the baseline arguments for continuity and spatial displacement.

```{r source-07, results='asis'}
# Iterates through the 'figures_07' list passed from the parent script
if (exists("figures_07")) {
    for (fig in figures_07) {
        cat(paste0("## ", fig$id, ": ", fig$title, "\n\n"))

        if (file.exists(fig$path)) {
            cat(paste0("![](", fig$path, ")\n\n"))
        } else {
            cat("**Image not found.**\n\n")
        }

        cat(paste0("**Explanation**: ", fig$explanation, "\n\n"))
        cat("\\newpage\n\n")
    }
}
```

# Section 2: Advanced Verification (Source 08)

These figures use advanced statistical techniques (rolling volatility, STL decomposition) to verify the "continuity" hypothesis.

```{r source-08, results='asis'}
if (exists("figures_08")) {
    for (fig in figures_08) {
        cat(paste0("## ", fig$id, ": ", fig$title, "\n\n"))

        if (file.exists(fig$path)) {
            cat(paste0("![](", fig$path, ")\n\n"))
        } else {
            cat("**Image not found.**\n\n")
        }

        cat(paste0("**Explanation**: ", fig$explanation, "\n\n"))
        cat("\\newpage\n\n")
    }
}
```

# Section 3: Expanded Analysis (Source 09)

These figures cover the 2010-2025 period with updated data and include specific checks for seasonality and category breakdowns. Note: Figure IDs start from E to avoid overlap.

```{r source-09, results='asis'}
if (exists("figures_09")) {
    for (fig in figures_09) {
        cat(paste0("## ", fig$id, ": ", fig$title, "\n\n"))

        if (file.exists(fig$path)) {
            cat(paste0("![](", fig$path, ")\n\n"))
        } else {
            cat("**Image not found.**\n\n")
        }

        cat(paste0("**Explanation**: ", fig$explanation, "\n\n"))
        cat("\\newpage\n\n")
    }
}
```

# Section 4: Spatial Trajectories (Source 10)

Analysis of the "Center of Gravity" for political violence incidents.

```{r source-10, results='asis'}
if (exists("figures_10")) {
    for (fig in figures_10) {
        cat(paste0("## ", fig$id, ": ", fig$title, "\n\n"))

        if (file.exists(fig$path)) {
            cat(paste0("![](", fig$path, ")\n\n"))
        } else {
            cat("**Image not found.**\n\n")
        }

        cat(paste0("**Explanation**: ", fig$explanation, "\n\n"))
        cat("\\newpage\n\n")
    }
}
```
